Formal Verification of Forward Secrecy and Post-Compromise Security for TreeKEM

### 2024-10-05 manuscript/manuscript-SBMF.tex
Updating repository citation

The \Promela encoding \footnote{Source code: \url{https://github.com/recursion-ninja/Manuscript-2024-SBMF}} of \CGKAmodN{N} produces all possible states and transitions of TreeKEM, and this representation is then supplied to a model checker for verification.

>>>>

The \Promela encoding~\cite{WashburnModelSPIN2024} \footnote{Source code: \url{https://github.com/recursion-ninja/Manuscript-2024-SBMF}} of \CGKAmodN{N} produces all possible states and transitions of TreeKEM, and this representation is then supplied to a model checker for verification.
